---
title: "36-315 Homework 11, Spring 2018"
author: "[bryanyan, jzh1, zongchuy, juliek1]"
date: "Due Wednesday, April 25, 2018 (11:59pm) on Canvas"
output: 
  html_document:
    toc:  true
    toc_float:  true
    code_folding:  show
runtime: shiny
---

#  Homework 11: Interaction

***
***

***
***

# Problem 0

We used Google's R style guide.

This submission is for the following group:

Bryan Yan: bryanyan

Joshua Huang: jzh1

Zong Chu Austin Yu: zongchuy

Julie Kim: juliek1

***
***

```{r}
faithful$week <- rep(c("Week 1", "Week 2"), each = 136)
```

# Problem 1: Shiny Outputs

(20 points)

We will practice running a Shiny app and converting base R graphs to `ggplot2` equivalents.

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

*a. (0 points)  Run the existing app by clicking the "Run Document" button in RStudio. Play with the two inputs (dropdown and slider). Can you find a combination of histogram binwidth and density bandwidth adjustment for which the histogram and density plot look similar?*

```{r base_r, echo=FALSE}
shinyApp(
  
  ui = fluidPage(
    inputPanel(
      selectInput("n_breaks", label = "Number of bins:",
                  choices = c(10, 20, 35, 50), selected = 20),
  
      sliderInput("bw_adjust", label = "Bandwidth adjustment:",
                  min = 0.2, max = 2, value = 1, step = 0.2)
    ),
    
    plotOutput("geyser_plot")
  ),
  
  server = function(input, output) {
    output$geyser_plot <- renderPlot({
      hist(faithful$eruptions, probability = TRUE,
           breaks = as.numeric(input$n_breaks),
           xlab = "Time (minutes)", ylab = "Density",
           main = "Geyser eruption duration")
      
      dens <- density(faithful$eruptions, adjust = input$bw_adjust)
      lines(dens, col = "blue")
    })
  },
  
  options = list(height = 550)
)
```

A histogram binwidth of 20 and density plot bandwith of 0.2 makes the two plots
look similar. 

*b. (20 points)  Modify the code below, so that the histogram and density plot are drawn using `ggplot2` instead of base R graphics. You only need to replace what's inside `renderPlot({...})`.*

* *Make a single call to `ggplot()`, specifying the `faithful` dataset. Map the `eruptions` variable to the x aesthetic, and map `..density..` to the y-aesthetic so the histogram and density plots will have the same scale.*
* *Add the two geoms. Use `input$n_breaks` and `input$bw_adjust` to specify the number of histogram bins and the density bandwidth adjustment.*
* *Make sure you have an appropriate title, axis labels, and data-source caption.*

```{r ggplot, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
shinyApp(
  
  ui = fluidPage(
    inputPanel(
      selectInput("n_breaks", label = "Number of bins:",
                  choices = c(10, 20, 35, 50), selected = 20),
  
      sliderInput("bw_adjust", label = "Bandwidth adjustment:",
                  min = 0.2, max = 2, value = 1, step = 0.2)
    ),
    
    plotOutput("geyser_plot")
  ),
  
  server = function(input, output) {
    output$geyser_plot <- renderPlot({
      ## PUT YOUR GGPLOT CODE HERE ##
      ggplot(faithful, aes(x = eruptions, y = ..density..)) +
        geom_histogram(bins = input$n_breaks) +
        geom_density(adjust = input$bw_adjust) +
        labs(title = "Geyser Eruption Duration",
             x = "Time (minutes)",
             y = "Density",
             caption = "Source: R Old Faithful Geyser Data")
    })
  },
  
  options = list(height = 550)
)
```

***
***

# Problem 2: Shiny Inputs

(30 points)

*We will continue to modify the example above. Now, add two more control "widgets" to allow extra inputs. The Shiny Tutorial's [Lesson 3](https://shiny.rstudio.com/tutorial/written-tutorial/lesson3/) has general advice about using widgets.*

* *Add a `radioButtons()` widget which lets you choose whether the `eruptions` or `waiting` variable should be plotted. Use `aes_string()` instead of `aes()` in your plot to use this input for your graph. (**Hint:** See Lecture 22 examples.)*  
*Also change the plot title depending on which variable is plotted. (**Hint:** Use `ifelse()` inside `labs()`.)*
* *Also add a `checkboxInput()` widget which lets you toggle whether or not a rug plot is added. (**Hint:** Save the plot without rugs using `p2 <- ggplot(...) + ...`; then use an `if` statement to add a rug to `p2` only if the checkbox was selected; and finally put `p2` as its own line of code to display the final graph.)*

```{r more_inputs, echo=FALSE, warning=FALSE, message=FALSE}
## COPY YOUR SOLUTION TO PROBLEM 1.B HERE, THEN MAKE THE REQUESTED CHANGES ##
shinyApp(
  
  ui = fluidPage(
    inputPanel(
      selectInput("n_breaks", label = "Number of bins:",
                  choices = c(10, 20, 35, 50), selected = 20),
  
      sliderInput("bw_adjust", label = "Bandwidth adjustment:",
                  min = 0.2, max = 2, value = 1, step = 0.2),
      
      radioButtons("which_variable", label = "Which variable?",
                   choices = c("Eruption Time (Mins)" = "eruptions",
                               "Waiting Time To Next Eruption (Mins)" = 
                                 "waiting")),
      
      checkboxInput("do_rug",  label = "Add Rug Plot")
    ),
    
    plotOutput("geyser_plot")
  ),
  
  server = function(input, output) {
    output$geyser_plot <- renderPlot({
      ## PUT YOUR GGPLOT CODE HERE ##
      p2 <- ggplot(faithful, aes_string(x = input$which_variable, 
                                  y = '..density..')) +
        geom_histogram(bins = input$n_breaks) +
        geom_density(adjust = input$bw_adjust) +
        labs(title = ifelse(input$which_variable == "eruptions", 
                            "Geyser Eruption Duration",
                            "Geyser Next Eruption Waiting Time Duration"),
             x = "Time (minutes)",
             y = "Density",
             caption = "Source: R Old Faithful Geyser Data")
      
      if(input$do_rug) {
        p2 <- p2 + geom_rug(aes(y = '..density..'))
      }
      
      p2
      
    })
  },
  
  options = list(height = 550)
)
```


***
***

# Problem 3: Plotly

(30 points)

*Plotly is a different way of making interactive plots. Most `ggplot` graphs can be saved and passed into the `ggplotly()` function to automatically get interactive zooming, panning, and tooltips on mouseover. Play with the plot below, then add these two extra features:*

* *Overlay scatterplot points on the graph using `geom_point()`. What information does Plotly display when you hover the mouse over a point? How about when you hover over the density contours but not over a point?*
* *Also facet the graph by `week`. Try to click & drag **only vertically**, to zoom in on a horizontal slice within one facet. What happens to the other facet? How about if you click & drag **only horizontally**?*  
*(Eventually, these two kinds of zoom should have the same effect, but apparently it is [still an open issue in Plotly's development](https://community.plot.ly/t/request-to-have-synchronized-axes-for-zoom-pan/3823).)*

```{r plotly, echo=FALSE, warning=FALSE, message=FALSE}
library(plotly)

p3 <- ggplot(faithful, aes(x = eruptions, y = waiting)) +
  stat_density_2d(aes(fill = ..level..), geom = "polygon") + 
  xlim(1, 6) + ylim(40, 100) + geom_point() +
  facet_grid(. ~ week)

ggplotly(p3)
```

+ When hovering over a point, Plotly displays the x and y coordinates of the point (i.e. eruptions and waiting values). When hovering over the density contours, Plotly displays the value of `level` at the specificed area.

+ When zooming on one slice vertically, the corresponding area on the other facet zooms as well. However, zooming horizontally on one facet does not affect the other. 


***
***

# Problem 4: Plotly within Shiny

(20 points)

*Finally, repeat your Shiny app from Problem 2. However, this time, use Plotly to render the graph, so that you have the best of both worlds: Shiny's interaction around the plot (selecting variables, toggling options, etc.), **and** Plotly's interaction within the plot itself (zooming, mouseover, etc.).*

*Simply copy the contents of your Problem 2 code block below, then make these changes:*

* *`plotOutput()` should become `plotlyOutput()`*
* *`renderPlot()` should become `renderPlotly()`*
* *As in Problem 3, save the ggplot output as `p4 <- ggplot(...) + ...`, and then call it using `ggplotly(p4)`*

```{r plotly_in_shiny, echo=FALSE, warning=FALSE, message=FALSE}
## COPY YOUR SOLUTION TO PROBLEM 2 HERE, THEN MAKE THE REQUESTED CHANGES ##
shinyApp(
  
  ui = fluidPage(
    inputPanel(
      selectInput("n_breaks", label = "Number of bins:",
                  choices = c(10, 20, 35, 50), selected = 20),
  
      sliderInput("bw_adjust", label = "Bandwidth adjustment:",
                  min = 0.2, max = 2, value = 1, step = 0.2),
      
      radioButtons("which_variable", label = "Which variable?",
                   choices = c("Eruption Time (Mins)" = "eruptions",
                               "Waiting Time To Next Eruption (Mins)" = 
                                 "waiting")),
# 
      checkboxInput("do_rug",  label = "Add Rug Plot")
    ),
    
    plotlyOutput("geyser_plot")
  ),
  
  server = function(input, output) {
    output$geyser_plot <- renderPlotly({
      ## PUT YOUR GGPLOT CODE HERE ##
      p4 <- ggplot(faithful, aes_string(x = input$which_variable, 
                                  y = '..density..')) +
        geom_histogram(bins = input$n_breaks) +
        geom_density(adjust = input$bw_adjust) +
        labs(title = ifelse(input$which_variable == "eruptions", 
                            "Geyser Eruption Duration",
                            "Geyser Next Eruption Waiting Time Duration"),
             x = "Time (minutes)",
             y = "Density",
             caption = "Source: R Old Faithful Geyser Data")
      
      if(input$do_rug) {
        p4 <- p4 + geom_rug(sides="b", aes(y = 'density'))
      }
      
      ggplotly(p4)
      
    })
  },
  
  options = list(height = 550)
)
```

***
***