---
title: "36-315 Lab 10, Spring 2018"
author: "Austin Yu (zongchuy), Bryan Yan (bryanyan), Josh Huang (jzh1), Julie Kim (juliek1)"
date: "Due Friday, April 27, 2018 (6:30pm) on Canvas"
output: 
  html_document:
    toc:  true
    toc_float:  true
    code_folding:  show
  html_notebook: 
    toc: yes
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Load-In
===
+ Load necessary libraries
+ Load data from `data.csv`
+ Check dimensions of the data, expecting a 3441197 x 7 dataframe
+ Return the first 5 rows
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(dplyr)
library(plyr)
library(shiny)
library(rsconnect)
library(ggplot2)
library(igraph)
library(ggraph)
library(ggmap)
library(maps)
library(plotly)

data = read.csv("data.csv")

dim(data)
head(data, 5)
```


Data Manipulation
===

+ Write a `date.to.month()` helper function, which takes in a date in the form YEAR-MONTH-DAY and converts it to a month
+ E.g. date.to.month(2017-01-26) returns January
+ Apply `date.to.month()` across the `Date` column of our data, creating a new column `Month`
```{r}
date.to.month = function(date) {
  date = as.character(date)
  month.numeric = as.numeric(unlist(strsplit(date, "-")))[2]
  return(month.name[month.numeric])
}

data$Month = sapply(data$Date, date.to.month)
```

+ Create a vector of countries based off of the country codes that we have in our `Region` column
+ Write a `code.to.country()` function that takes in a country code and returns the country
+ E.g. `code.to.country("ec")` returns "Ecuador"
+ Apply `code.to.country()`across the `Region` column of our data, creating a new column `Country`
```{r}
countries = unique(data$Region)
names(countries) = c("Ecuador", "France", "Argentina", "Finland", "Norway", 
                     "Italy", "Lithuania", "Philippines", "Taiwan", 
                     "New Zealand", "Estonia", "Turkey", 
                     "USA", "El Salvador", "Costa Rica", 
                     "Germany", "Chile", "Japan", "Brazil", "Honduras", 
                     "Guatemala", "Switzerland", "Hungary", "Canada", "Peru", 
                     "Belgium", "Malaysia", "Denmark", "Bolivia", "Poland", 
                     "Austria", "Portugal", "Sweden", "Mexico", "Panama", 
                     "Uruguay", "Iceland", "Spain", "Czech Republic", "Ireland", 
                     "Netherlands", "Slovakia", "Colombia", "Singapore", 
                     "Indonesia", "Dominican Republic", "Luxembourg", 
                     "UK", "World", "Paraguay", "Australia", 
                     "Latvia", "Greece", "Hong Kong")

code.to.country = function(code) {
  code = as.character(code)
  return(names(countries)[which(countries == code)])
}

data$Country = sapply(data$Region, code.to.country)
```

+ Create a vector of continents based off of the countries that we have in our `Country` column
+ Write a `country.to.continent()` function that takes in a country code and returns the continent
+ E.g. `country.to.continent("Ecuador")` returns "South America"
+ Apply `country.to.continent()`across the `Country` column of our data, replacing the column `Region`
```{r}
asia = c("Philippines", "Taiwan", "Japan", "Malaysia", "Singapore", "Indonesia", 
         "Hong Kong")
europe = c("France", "Finland", "Norway", "Italy", "Lithuania", "Estonia", 
           "Turkey", "Germany", "Switzerland", "Hungary", "Belgium", "Denmark", 
           "Poland", "Austria", "Portugal", "Sweden", "Iceland", "Spain", 
           "Czech Republic", "Ireland", "Netherlands", "Slovakia", "Luxembourg", 
           "United Kingdom", "Latvia", "Greece")
northamerica = c("USA", "Canada", "Mexico")
centralamerica = c("El Salvador", "Costa Rica", "Honduras", "Guatemala", 
                   "Panama", "Dominican Republic")
southamerica = c("Ecuador", "Argentina", "Chile", "Brazil", "Peru", "Bolivia", 
                 "Uruguay", "Colombia", "Paraguay")
oceania = c("New Zealand", "Australia")

country.to.continent = function(country) {
  country = as.character(country)
  if (country %in% asia) return("Asia")
  if (country %in% europe) return("Europe")
  if (country %in% northamerica) return("North America")
  if (country %in% centralamerica) return("Central America")
  if (country %in% southamerica) return("South America")
  if (country %in% oceania) return("Oceania")
  return(NA)
}

data$Region = sapply(data$Country, country.to.continent)
```

+ Statistical summaries to get a sense of the data
```{r}
# Summary statistics on top 200 streams, world wide
streams = summary(data$Streams)
# Summary statistics on top 200 streams, by country
streams.by.country = ddply(data, .(Country), function(x) summary(x$Streams))
# Summary statistics on top 200 streams, by continent
streams.by.cont = ddply(data, .(Region), function(x) summary(x$Streams))

# Total streams, world wide
tot.streams = sum(as.numeric(data$Streams))
# Summary statistics on top 200 streams, by country
tot.streams.by.country = ddply(data, .(Country), 
                               function(x) sum(as.numeric(x$Streams)))
# Summary statistics on top 200 streams, by continent
tot.streams.by.cont = ddply(data, .(Region), 
                            function(x) sum(as.numeric(x$Streams)))

# How many times did Artists end up in the top 200 rankings, world wide?
artists = as.data.frame(table(data$Artist))
# How many times did Artists end up in the top 200 rankings, by country?
artists.by.country = ddply(data, .(Country), function(x) table(x$Artist))
# How many times did Artists end up in the top 200 rankings, by continent?
artists.by.cont = ddply(data, .(Region), function(x) table(x$Artist))

# How many unique Artists are there in the top 200 rankings, world wide?
n.artists = nrow(artists)
# How many times did Artists end up in the top 200 rankings, by country?
n.artists.by.country = ddply(artists.by.country, .(Country), 
                             function(x) sum(x != 0))
# How many times did Artists end up in the top 200 rankings, by continent?
n.artists.by.cont = ddply(artists.by.cont, .(Region), 
                          function(x) sum(x != 0))

# How many times did tracks end up in the top 200 rankings, world wide?
tracks = as.data.frame(table(data$Track.Name))
# How many times did tracks end up in the top 200 rankings, by country?
tracks.by.country = ddply(data, .(Country), function(x) table(x$Track.Name))
# How many times did tracks end up in the top 200 rankings, by continent?
tracks.by.cont = ddply(data, .(Region), function(x) table(x$Track.Name))

# How many unique Artists are there in the top 200 rankings, world wide?
n.tracks = nrow(tracks)
# How many times did Artists end up in the top 200 rankings, by country?
n.tracks.by.country = ddply(tracks.by.country, .(Country), 
                             function(x) sum(x != 0))
# How many times did Artists end up in the top 200 rankings, by continent?
n.tracks.by.cont = ddply(tracks.by.cont, .(Region), 
                          function(x) sum(x != 0))
```


Graphics
===

Set Up for Graph 1
---
+ Create the `country.data` dataframe that consolidates the number of streams, tracks and artists of each country into one table
+ Use `map_data` to add goegraphical data for our map graphic 
```{r}
data.asia = data[which(data$Region == "Asia"),]
data.europe = data[which(data$Region == "Europe"),]
data.northamerica = data[which(data$Region == "North America"),]
data.centralamerica = data[which(data$Region == "Central America"),] 
data.southamerica = data[which(data$Region == "South America"),] 
data.oceania = data[which(data$Region == "Oceania"),] 

colnames(tot.streams.by.country)[2] = "Total_Streams"
country.data = tot.streams.by.country

colnames(n.artists.by.country)[2] = "N_Artists"
country.data = left_join(country.data, n.artists.by.country, 
                         by = "Country")

colnames(n.tracks.by.country)[2] = "N_Tracks"
country.data = left_join(country.data, n.tracks.by.country, 
                         by = "Country")

country.data = left_join(country.data, artists.by.country, 
                         by = "Country")

coords = map_data("world")
coords$Country = coords$region
coords = coords[,c("Country", "long", "lat", "group")]

country.data = left_join(country.data, coords, by = c("Country"))
```

Graph 1
---
Compare the Countries by:

    + Number of streams 
    + Number of top tracks listened to 
    + Number of top artists listeed to (do they tend to listen to more top tracks by the same artists)
```{r, echo = FALSE, warning = FALSE, message = FALSE}
shinyApp(
  ui = fluidPage(
    inputPanel(
       radioButtons("variable", label = "Fill Variable:",
                   choiceNames = c("Number of Streams", "Number of Tracks", 
                                   "Number of Artists"),
                   choiceValues = c("Total_Streams", "N_Tracks", "N_Artists"))
    ),
    plotlyOutput("world_map")
  ),
  
  server = function(input, output) {
    output$world_map <- renderPlotly({
      
      rplot = ggplot() + 
        geom_polygon(data = coords, aes(x = long, y = lat, group = group), 
                     fill = "white") +
        geom_polygon(data = country.data, aes_string(x = "long", y = "lat", 
                                                     group = "group",
                                                     fill = input$variable)) + 
        scale_fill_gradient2(high = "brown", low = "purple", mid = "white") +
        labs(title = "Top 200 ranking Spotify tracks worldwide",
             x = "", 
             y = "") +
        theme(axis.text.x = element_blank(),
              axis.text.y = element_blank())
      
      if(input$variable == "Total_Streams") 
        rplot = rplot + labs(fill = "Number of Streams")
      if(input$variable == "N_Tracks") 
        rplot = rplot + labs(fill = "Number of Tracks")
      if(input$variable == "N_Artists") 
        rplot = rplot + labs(fill = "Number of Artists")
      
      ggplotly(rplot)
      
      })
  },
  options = list(height = 550)
)
```

Graph 2: INCOMPLETE
---
```{r, eval = FALSE, include = FALSE}
shinyApp(
  
  ui = fluidPage(
    inputPanel(
      selectInput("continent", label = "Continent:",
                  choices = c("Asia", "Europe", "Central America", 
                              "North America", "Oceania", "South America", 
                              "World"), 
                  selected = "Asia"),
      
      selectInput("artist", label = "Top 200 Artist:",
                  choices = artists, selected = "-M-")
    ),
    
    plotOutput("cont_map")
  ),
  
  server = function(input, output) {
    output$cont_map <- renderPlot({
      
      ggplot() + 
        geom_polygon(data = coords, aes(x = long, y = lat, group = group), 
                     fill = "white") + 
        geom_polygon(data = country.data, aes(x = long, y = lat, group = group,
                                              fill = Total_Streams)) +
        scale_color_gradient()

    })
  }
  
)
```

GRAPH 3: COMPLETE (Can Add More Features)
---
```{r}
shinyApp(
  
  ui = fluidPage(
    inputPanel(
      selectInput("country", label = "Country",
                  choices = unique(data$Country), 
                  selected = "United States of America"),
      
      selectInput("country2", label = "Country 2",
                  choices = unique(data$Country),
                  selected = "Canada"),
      
      textInput("song", label = "Song Name", 
                     value = "rockstar"),
      
      textInput("artist", label = "Artist Name", 
                     value = "Post Malone")
    ),
    
    plotOutput("top_ranking_time")
  ),
  
  server = function(input, output) {
    
    dataSub <- reactive({
        if (input$song == "") {
          chosenSong <- " "
        }
        else {
          chosenSong <- input$song 
        }
        subset(data, Track.Name == chosenSong &
               Artist == input$artist &
              (Country == input$country | Country == input$country2))
    })
    
    output$top_ranking_time <- renderPlot({
      subsetOfData <- dataSub()
      if (nrow(subsetOfData) == 0) {
        ggplot() + 
          annotate("text", 
                   x = 4, y = 25, size = 8, label = "Song/Artist Not Found") + 
          theme_void() +
          labs(x = NULL, y = NULL)
      }
      else {
        ggplot(subsetOfData, aes(x = as.Date(Date), y = Streams, 
                                 color = Country, group = Country)) +
          scale_x_date(date_labels = "%b %y") +
          scale_y_continuous(labels = comma) +
          geom_point() +
          geom_line() +
          labs(title = "Song Streams by Country Over Time",
                x = "Date",
                y = "Number of Streams") +
          theme(axis.title.y = 
                  element_text(margin = margin(r = 20)),
                axis.title.x =
                  element_text(margin = margin(t = 20)))
      }
    })
  },
  
  options = list(height = 550)
)
```