---
title: "36-315 Lab 10, Spring 2018"
author: "Austin Yu (zongchuy), Bryan Yan (bryanyan), Josh Huang (jzh1), Julie Kim (juliek1)"
date: "Due Friday, April 27, 2018 (6:30pm) on Canvas"
output: 
  html_document:
    toc:  true
    toc_float:  true
    code_folding:  show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Data Overview
===
**Context**

Music streaming is ubiquitous. Currently, Spotify plays an important part on that. This dataset enable us to explore how artists and songs' popularity varies in time.

**Content**

This dataset contains the daily ranking of the 200 most listened songs in 53 countries from 2017 and 2018 by Spotify users. It contains more than 2 million rows, which comprises 6629 artists, 18598 songs for a total count of one hundred five billion streams count.

The data spans from 1st January 2017 to 9th January 2018 and will be kept up-to-date on following versions. It has been collected from Spotify's regional chart data.

**Inspiration**

Can you predict what is the rank position or the number of streams a song will have in the future?
How long does songs "resist" on the top 3, 5, 10, 20 ranking?
What are the signs of a song that gets into the top rank to stay?
Do continents share same top ranking artists or songs?
Are people listening to the very same top ranking songs on countries far away from each other?
How long time does a top ranking song takes to get into the ranking of neighbor countries?

**Questions**

1) Do people listen to the same songs even if the country is far away from each other?
2) What is the most popular song based on region?
3) How long does a particular song stay in top 5/10/20?
4) Given a top ranking song in a particular region, how long before a neighboring country has the same song in its top rankings?


Code
===
+ Load necessary libraries
+ Load data from `data.csv`
+ Check dimensions of the data, expecting a 3441197 x 7 dataframe
+ Return the first 5 rows
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(dplyr)
library(plyr)
library(shiny)
library(rsconnect)
library(ggplot2)
library(igraph)
library(ggraph)
library(ggmap)
library(maps)
library(sp)

data = read.csv("data.csv")

dim(data)
head(data, 5)
```

+ Write a `date.to.month()` helper function, which takes in a date in the form YEAR-MONTH-DAY and converts it to a month
+ E.g. date.to.month(2017-01-26) returns January
+ Apply `date.to.month()` across the `Date` column of our data, creating a new column `Month`
```{r}
date.to.month = function(date) {
  date = as.character(date)
  month.numeric = as.numeric(unlist(strsplit(date, "-")))[2]
  return(month.name[month.numeric])
}

data$Month = sapply(data$Date, date.to.month)
```

+ Create a vector of countries based off of the country codes that we have in our `Region` column
+ Write a `code.to.country()` function that takes in a country code and returns the country
+ E.g. `code.to.country("ec")` returns "Ecuador"
+ Apply `code.to.country()`across the `Region` column of our data, creating a new column `Country`
```{r}
countries = unique(data$Region)
names(countries) = c("Ecuador", "France", "Argentina", "Finland", "Norway", "Italy", "Lithuania", "Philippines", "Taiwan", "New Zealand", "Estonia", "Turkey", "United States of America", "El Salvador", "Costa Rica", "Germany", "Chile", "Japan", "Brazil", "Honduras", "Guatemala", "Switzerland", "Hungary", "Canada", "Peru", "Belgium", "Malaysia", "Denmark", "Bolivia", "Poland", "Austria", "Portugal", "Sweden", "Mexico", "Panama", "Uruguay", "Iceland", "Spain", "Czech Republic", "Ireland", "Netherlands", "Slovakia", "Colombia", "Singapore", "Indonesia", "Dominican Republic", "Luxembourg", "United Kingdom", "World", "Paraguay", "Australia", "Latvia", "Greece", "Hong Kong")

code.to.country = function(code) {
  code = as.character(code)
  return(names(countries)[which(countries == code)])
}

data$Country = sapply(data$Region, code.to.country)
```




